# Model simulation


## Simulation periods and warmups

A quiescent start condition was adopted for velocity and water levels. Initialisation of salinity and temperature data was based on spatially variable ROMS data as described earlier. The simulations were then warmed-up for at least 21 days prior to all modelling tasks and result analysis, to develop the internal salinity and temperature distributions contributing to density stratification.


For each of the model scenarios, the models were run for 52 days excluding the warmup periods and Model outputs were extracted at every 15 minutes. Calibration period was selected based on measured data availability and the hydrodynamics were simulated for the one whole year; 

* Calibration period: 01/01/2013 to 01/03/2013

* Simulation period: 01/01/2013 to 31/12/2013


Modeled data were compared against observed data (Figure \@ref(fig:CS-met))including;

* Velocity data at S01 and S02 sites from JPPL 

* Temperature and salinity data at Stirling and Parmelia from Fremantle Ports Authority

* Temperature and salinity data at the Central Buoy and South Buoy stations from Water Corporation


## Water level





## Velocity comparison

Comparisons between simulated velocities and ADCP measurements in the calibration at S01 and S02 were carried out. Measured data at different depths were compared with modeled data for the calibration periods.


The line plots shown in Figure 5-1 and Figure 5-2 demonstrate that the model reproduced the key characteristics of the velocity field at the different stations.



The model predictive skill was also tested statistically with calculations of the Index of Agreement (IOA), Mean Absolute Error (MAE), and Root Mean Square Error (RMSE). At project inception, the following calibration targets were agreed as indicators of satisfactory model validation (Table \@ref(tab:calibgoal-tab)):



```{r calibgoal-tab,echo=FALSE,escape = FALSE,}
calib_goal<-read.csv(file="table/velocity_calib_goal.csv")

knitr::kable(calib_goal, booktabs = TRUE, caption = 'Calibration goals for velocity',
             col.names = c("Variable","IOA (-)","MAE (m/s)","RMSE (m/s)"))
```

This statistical evaluation of the predicted currents at the ADCP locations is provided in Table \@ref(tab:caliba-tab), Table \@ref(tab:calibb-tab), Table \@ref(tab:calibc-tab) and Table \@ref(tab:calibd-tab) for S01 and S02 for different time periods.


```{r caliba-tab,echo=FALSE,escape = FALSE,}
calib_a<-read.csv(file="table/a_timeperiod_Westport_stats.csv")

knitr::kable(calib_a, booktabs = TRUE, caption = 'Summary of model predictive skill statistics for 
             currents at S01 and S02 for the time period a',
             #table.attr = "style='width:40%;'" ,
             format="html",
             col.names = c("Site","Layer type","IOA Vx","IOA Vy", "RMSE Vx","RMSE Vy", 
                           "MAE Vx", "MAE Vy"))%>%
              #col.names = c("Site","Layer type","IOA Vx","IOA Vy", "RMSE Vx","RMSE Vy", 
                          # "MAE Vx", "MAE Vy","BIAS Vx", "BIAS Vy","$R^{2}$ Vx","$R^{2}$ Vy"))%>%
              #kable_classic(full_width = T, position = "center", )
              kable_paper("hover", full_width = F)
```

```{r calibb-tab,echo=FALSE,escape = FALSE,}
calib_b<-read.csv(file="table/b_timeperiod_Westport_stats.csv")

knitr::kable(calib_b, booktabs = TRUE,  caption = 'Summary of model predictive skill statistics for 
             currents at S01 and S02 for the time period b',
             col.names = c("Site","Layer type","IOA Vx","IOA Vy", "RMSE Vx","RMSE Vy", 
                           "MAE Vx", "MAE Vy"))%>%
              kable_paper("hover", full_width = F)
#%>% 
      #kable_styling(latex_options="scale_down")
             

```


```{r calibc-tab,echo=FALSE,escape = FALSE,}
calib_c<-read.csv(file="table/c_timeperiod_Westport_stats.csv")

knitr::kable(calib_c, booktabs = TRUE, caption = 'Summary of model predictive skill statistics for 
             currents at S01 and S02 for the time period c',
             col.names = c("Site","Layer type","IOA Vx","IOA Vy", "RMSE Vx","RMSE Vy", 
                           "MAE Vx", "MAE Vy"))%>%
              kable_paper("hover", full_width = F)
```


```{r calibd-tab,echo=FALSE,escape = FALSE,}
calib_d<-read.csv(file="table/d_timeperiod_Westport_stats.csv")

knitr::kable(calib_d, booktabs = TRUE, caption = 'Summary of model predictive skill statistics for 
             currents at S01 and S02 for the time period d',
             col.names = c("Site","Layer type","IOA Vx","IOA Vy", "RMSE Vx","RMSE Vy", 
                           "MAE Vx", "MAE Vy"))%>%
              kable_paper("hover", full_width = F)
```

## Temperature


## Salinity


# References